---
title: "Using models 1"
author: "Devon Parsons"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: darkly
  pdf_document:
    toc: yes
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
require(here)

catrate <- read.csv(here("data", "catrate.csv"))

head(catrate)

summary(catrate)
```

# #1 
```{r}
hist(catrate$cat.rate, main = "Salamander Reproduction Catastrophic Rates", xlab = "Catastrophe Rate")
```


# #2
```{r}
shapiro.test(catrate$cat.rate)
```
# #3 
Null hypothesis- the data were sampled from a normally distributed population

# #4
If I made a significance value of 0.05, the p-value is smaller than that value meaning its very likely our sample came from a non normally distributed population. 

# #5
```{r}
t.test(x = catrate$cat.rate, mu = 0.28, alternative = "greater")
t.test(x = catrate$cat.rate, mu = 0.28, alternative = "less")

```
# #6
The null hypothesis for the t test is that the catastrophic rate is the same as the pond-late filling rate. 

# #7
This is a one-tailed test, as I tested for the possibility of the relationship being greater than. P value is smaller than .05 

# #8
p-value = 0.01054

# #9
0.3526250 0.7261295

# #10
Since the p-value is much smaller than the significance value of .05, I can conclude that there is strong evidence to reject the null hypothesis. 

# #11
```{r}
wilcox.test(catrate$cat.rate, mu = 2 / 7)
```

# #12
p value from Wilcox test is 0.006275, and the value from the t.test is 0.01054. If we have a significance value of 0.05, both of these are less than that so we could reject our null. But if it was 0.01, the Wilcox test would reject our null and the t.test would not be able to reject our null. 

# #13
Since the p-value from the Wilcox test (.006275) is smaller than our significance value of .05, there is strong evidence to reject the null hypothesis. 

# #14
The result from the one-sample t test tells us that the true mean is not equal to .28, but is actually .5393. 
The Wilcoxon rank sum test tells us the true mean is not equal to 0.28, but does not tell us the true mean value. Both tests signify that there is strong evidence the null hypothesis can be rejected. 

# #15
I think the Wilcoxon test is more appropriate for this data because it is intended for data that is not normally distributed, whereas the t test is best for non normally distributed data.

# #16
```{r}
require(palmerpenguins)
dat_penguins = droplevels(subset(penguins, species != "Gentoo"))
dat_chinstrap <- subset(dat_penguins, species == "Chinstrap")
shapiro.test(dat_chinstrap$flipper_length_mm)
```


```{r}
dat_adelie <- subset(dat_penguins, species == "Adelie")
shapiro.test(dat_adelie$flipper_length_mm)
```

# #17
The p value for Chinstrap is .8106, and for Adelie it is .72. Both of the p values are larger than the significance value of .05, so we can not reject the null hypothesis. We can conclude that for both species, the flipper lengths are normally distributed. 

# #18
```{r}
par(mfrow = c(1, 2))
hist(dat_adelie$flipper_length_mm, main = "Adelie Penguin Flipper Length", xlab = "flipper length")
hist(dat_chinstrap$flipper_length_mm, main = "Chinstrap Penguin Flipper Length", xlab = "flipper length")

```
# #19
The alternative hypothesis is that the flipper length between the Adelie and Chinstrap penguins are not the same. This is a two tailed test because a direction is not specified, like if the flipper length is greater or less than a certain number. 

# #20
```{r}
t.test(dat_penguins$flipper_length_mm ~ dat_penguins$species)
```





